SoK: Transparent Dishonesty. Front-running attacks on Blockchain.

### 2018-12-06 frontrunning/Latex/sections/paper.tex
[frontrunning] reorganize solutions

@@

\section{How to stop Front-running?} %We have the applicability of the solutions inline.

@@

There are two main approaches to mitigating front-running on blockchains: one is to design a blockchain that is front-run resistant, and the other to design the application logic in a way that front-running is not profitable. This can be done in addition to any legal remedies that might be enforceable (See Appendix ~\ref{app:traditionalprevention}). We note, but consider out-of-scope, approaches that introduce trusted parties to centralize time-sensitive functionalities (\eg exchanges \textit{EtherDelta} and \textit{0xProject} use off-chain order books~\cite{warren20170x,0xfrontrunning:online}).

@@

\subsection{Front-Running Resistant Blockchains}
In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running. Note that, the existing technical difficulties make these solutions hard to achieve as it requires designers to test edge case scenarios.

@@

@@

%The first solution was to prevent front-running, but then it was attacked so they updated the solution. this new solution also could be attacked. 
\paragraph{Design Decision \#3: Dual Authoring.} This scheme is proposed to solve the front-running issue within Loopring -- a decentralized exchange protocol proposed by Wang~\etal~\cite{wang2018loopring}. In the first version of this protocol, orders are grouped in \emph{ring orders} once they are sent by the users. After the required signatures are provided by the \textit{ring miner}, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}). While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with higher gasPrice and his address instead of the ring miner's address. Using the proposed \textit{dual authoring} solution in the new version of Loopring, regeneration of the \emph{submitRing transaction} is infeasible as the users have to sign the orders using their secondary private keys (auth-keys), which are only known to the ring miner and not other users (see Figure~\ref{fig:not_vulnerable_loopring}).

\subsection{Application Design to Prevent Front-running}

Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.

@@

@@

>>>>

% Developers don't have the mindset to design DApps with front-running in mind. This is an attempt to bring forward the subject and make them more aware of these type of attacks

@@

\section{Key Mitigations} %We have the applicability of the solutions inline.

@@

We encounter a number of main approaches to mitigate front-running attacks on blockchains: we summerize the main approaches.

one is to design a blockchain that is front-run resistant, and the other to design the application logic in a way that front-running is not profitable. This can be done in addition to any legal remedies that might be enforceable (See Appendix ~\ref{app:traditionalprevention}). We note, but consider out-of-scope, approaches that introduce trusted parties to centralize time-sensitive functionalities (\eg exchanges \textit{EtherDelta} and \textit{0xProject} use off-chain order books~\cite{warren20170x,0xfrontrunning:online}).

@@

In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running. Note that, the existing technical difficulties make these solutions hard to achieve as it requires designers to test edge case scenarios.

%\subsection{Front-Running Resistant Blockchains}
\subsection{Transaction Queue}

@@

\subsection{Confidentiality}

@@

@@

%The first solution was to prevent front-running, but then it was attacked so they updated the solution. this new solution also could be attacked.

\subsection{Design Practices}

@@

\paragraph{Design Decision \#3: Dual Authoring.} This scheme is proposed to solve the front-running issue within Loopring -- a decentralized exchange protocol proposed by Wang~\etal~\cite{wang2018loopring}. In the first version of this protocol, orders are grouped in \emph{ring orders} once they are sent by the users. After the required signatures are provided by the \textit{ring miner}, he sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement (see Figure~\ref{fig:vulnerable_loopring}). While this transaction sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with higher gasPrice and his address instead of the ring miner's address. Using the proposed \textit{dual authoring} solution in the new version of Loopring, regeneration of the \emph{submitRing transaction} is infeasible as the users have to sign the orders using their secondary private keys (auth-keys), which are only known to the ring miner and not other users (see Figure~\ref{fig:not_vulnerable_loopring}).

%\subsection{Application Design to Prevent Front-running}
%
%Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.
